\cvsection{Extracurriculars}
\begin{cventries}
    \cventry
    {FB Messenger Chatbot that plays songs based on the user's desired mood}
    {Sentima}
    {Ongoing Side-Project}
    {Sept. 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Back-end on AWS processes user-input and generates an intent-URI, which tells Sentimize what songs to play}
      \end{cvitems}
    }
  \cventry
    {Lets people sort their local music based on how they want to feel}
    {Sentimize}
    {Ongoing Side-Project}
    {May. 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Analyzes the key, tempo, and pitch of songs as to predict their moods (C++, NDK, and Superpowered SDK)}
        \item {SQLite database caching. Made with Material Design in Android Studio. Published on Google Play}
      \end{cvitems}
    }
  \cventry
    {Don Mills Online Judge}
    {\href{https://dmoj.ca/user/Sentient/solved}{Don Mills Open Programming Contest Problem-Setter}}
    {Don Mills Collegiate Institute}
    {Sep. 2014 - June. 2015}
    {
      \begin{cvitems}
        \item {Wrote algorithmic problems (graph-search, sorting, DP, greedy, etc.) for the DMOPC, which was held monthly and written by about 150 students from across Ontario}
        \item {Was a lead-organizer of the Don Mills Programming Gala, an on-site programming contest attended by 120 students}
      \end{cvitems}
    }
  \cventry
    {Hack The North}
    {iHear}
    {University of Waterloo}
    {Sep. 14. 2016 - Sept. 16. 2016}
    {
      \begin{cvitems}
        \item {Built sound-localization component of a VR-headset intended to allow deaf people to feel more connected to their surroundings}
        \item {Mounted microphones that were connected to an Arduino on the headset, which then streamed audio to the back-end via a TCP socket. The stream was then processed in JS and the results were pushed to the headset (Unity on Google Cardboard)}
      \end{cvitems}
    }
   \cventry
    {PennApps XIII}
    {HackTogether}
    {University of Pennsylvania}
    {Jan. 26. 2016 - Jan. 28. 2016}
    {
      \begin{cvitems}
        \item {Built Android app (in Android Studio) where hackers entered their interests and skills and then placed them into teams}
        \item {Used Parse back-end and Python program to form the teams}
      \end{cvitems}
    }
    
\end{cventries}
